\section{Project}

\begin{itemize}
  \item \textbf{Title:} Paths and cycles enumeration methods in graphs
  \item \textbf{Length:} Medium (175 hours)
\end{itemize}

% Project Synopsis: A short description and summary of its aim and scope.
\subsection{Project Synopsis}
The project is aimed to add some functionalities related to graph theory in
SageMath. Specifically, it aims to add the following objectives:

\begin{itemize}
  \item Add a method for the enumeration of simple cycles in undirected graphs, as
        there is already an implemented method for directed graphs. Then extend these
        methods to support enumeration of cycles by increasing weight.
  \item Implement recent and more efficient methods for finding the k shortest simple
        paths in (un) weighted (di) graphs.
  \item Unify the input and output of these methods to ensure similar behaviors.
\end{itemize}

\subsection{Personal involvement}
% What is your personal involvement or relationship with your proposed project?
During my competitive programming experience, I was exposed to many areas of
mathematics, including graph theory, which I found especially interesting. I
became the team member with the most training and strength in graph theory on
my competitive programming team. When I saw this project idea, I felt it was
the perfect fit for me. I am confident that I have solved variations of the
problems in this project during my training and in official contests. In
addition, my experience in setting and testing problems has given me the skills
needed to work on graph theory challenges.

\input{Project/Details/Details.tex}

\input{Project/Schedule.tex}

% Risk Management: 
% Try to anticipate potential problems and explain, 
% how to mitigate them. 
% Propose alternative scenarios,
% if a particular milestone isn't reached, 
% to still successfully complete the project.

\subsection{Risk Management}
While I believe I am well-suited for this project, I have identified several
potential risks that could impact the project:

\begin{enumerate}
  \item Some parts of this project depend on modules that are already implemented (like
        trees and other data structures). I might face problems with these modules,
        such as bugs or unexpected behavior. In the best case, I will be able to fix
        the issues in these modules and continue with the project as planned. In the
        worst case, I will write a temporary implementation to replace the broken
        module. This might cause some code duplication, but it will let me continue
        working until the original module is fixed.

  \item Delays might happen due to either unexpected bugs or limitations. When drafting
        the project schedule, I made sure to give extra time for each phase. However,
        in worst case scenario, the order of the phases in the schedule guarantees that
        a big part of the project will be done.

\end{enumerate}